SST_patterns

### 2020-04-06 SST_patterns.Rmd
update

metric_4years <- combined_products %>% 
   filter(year(date_start) %in% 2011:2014)

@@

lmod <- lm(mean_intensity ~ mean_dur, data = metrics)
summary(lmod)

glht(lmod, linfct = K)

>>>>

metric_4years <- combined_products %>% 
   filter(year(date_start) %in% 2011:2014) # only for the years 2011-2014 so 4 year period

@@

# lmod <- lm(mean_intensity ~ mean_dur, data = metrics)
# summary(lmod)
# 
# glht(lmod, linfct = K)
